QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-2.2.tex
uniform wording for b&b
revise bibliography
- remove two duplicates
- fix some capitalizations
- no space in pages
- full journal names
- add missing issue/number
- fix some typos

 \item \emph{Nonconvex Continuous Quadratic Programs} \textit{QCQ} are generally $\mathcal{NP}$-hard, even if the constraints are very specific (\textit{QCB}) and only a single eigenvalue of $Q^0$ is negative \cite{Hemmecke2010}. They therefore require enumerative techniques, such as spatial Branch\&Bound \cite{FV90,BeLeLiMaWa08}, to be solved to optimality. Of course, local approaches are available that are able to efficiently provide saddle points (hopefully, local optima) of the \textit{CQC}, but providing global guarantees about the quality of the obtained solutions is challenging. In our library we have specifically focused on  \emph{exact} solution of the instances.

@@

  \item \emph{Nonconvex Binary Quadratic Programs} \textit{QB}\{\textit{B},\textit{N},\textit{L}\} obviously are $\mathcal{NP}$-hard. However, the special nature of binary variables combined with quadratic forms allows for quite specific techniques to be developed, one of which is the reformulation of the problem as a \textit{LBL}. Also, many well-known combinatorial problems can be naturally reformulated as problems of this class, and therefore a considerable number of results have been obtained by exploiting specific properties of the set of constraints \cite{Rendl2008,Loiola2007657}.

>>>>

 \item \emph{Nonconvex Continuous Quadratic Programs} \textit{QCQ} are generally $\mathcal{NP}$-hard, even if the constraints are very specific (\textit{QCB}) and only a single eigenvalue of $Q^0$ is negative \cite{Hemmecke2010}. They therefore require enumerative techniques, such as spatial Branch-and-Bound \cite{FV90,BeLeLiMaWa08}, to be solved to optimality. Of course, local approaches are available that are able to efficiently provide saddle points (hopefully, local optima) of the \textit{CQC}, but providing global guarantees about the quality of the obtained solutions is challenging. In our library we have specifically focused on  \emph{exact} solution of the instances.

@@

  \item \emph{Nonconvex Binary Quadratic Programs} \textit{QB}\{\textit{B},\textit{N},\textit{L}\} obviously are $\mathcal{NP}$-hard. However, the special nature of binary variables combined with quadratic forms allows for quite specific techniques to be developed, one of which is the reformulation of the problem as a \textit{LBL}. Also, many well-known combinatorial problems can be naturally reformulated as problems of this class, and therefore a considerable number of results have been obtained by exploiting specific properties of the set of constraints \cite{Rendl2008,loiola-etal:2007}.

### 2018-02-08 methods.tex
mosek, gurobi, xpress don't run on QGQ
xpress and gurobi can also to nonconvex objective if binary variables only
alphabetic order of solvers
revise bibliography
- remove two duplicates
- fix some capitalizations
- no space in pages
- full journal names
- add missing issue/number
- fix some typos

Nearly all of the complete solvers in Table \ref{t:solvers} that address $\mathcal{NP}$-hard problems (i.e.~those in \textit{QGQ}$\smallsetminus$\textit{CCC}) are based on Branch-and-Bound (BB) \cite{land_doig}. When the BB algorithm is allowed to branch on coordinate directions corresponding to continuous variables, it is called \emph{spatial} BB (sBB) \cite{dakin,couenne}. BB algorithms require exponential time in the worst case, and their exponential behavior unfortunately often shows up in practice. They can also be used heuristically (forsaking their completeness guarantee) in a number of ways, e.g.~by terminating them early. The following solvers from Table \ref{t:solvers} implement complete BB algorithms for \textit{QGQ} or some subclasses: 
%
\begin{itemize}
 \item \antigone, \baron, \couenne, \lindo, \scip for \textit{QGQ};
 %
\item \cplex for \textit{QGL} and \textit{CGC};
%
 \item \knitro, \bonmin, \sbb, \xpress, \gurobi, and \mosek for \textit{CGC}.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for \textit{QGQ}. We also note that \lgo implements an incomplete BB algorithm for \textit{QCQ} by using bounds obtained from sampling.

>>>>

Nearly all of the complete solvers in Table \ref{t:solvers} that address $\mathcal{NP}$-hard problems (i.e.~those in \textit{QGQ}$\smallsetminus$\textit{CCC}) are based on Branch-and-Bound (BB) \cite{land_doig}. When the BB algorithm is allowed to branch on coordinate directions corresponding to continuous variables, it is called \emph{spatial} BB (sBB) \cite{dakin,BeLeLiMaWa08}. BB algorithms require exponential time in the worst case, and their exponential behavior unfortunately often shows up in practice. They can also be used heuristically (forsaking their completeness guarantee) in a number of ways, e.g.~by terminating them early. The following solvers from Table \ref{t:solvers} implement complete BB algorithms for \textit{QGQ} or some subclasses: 
%
\begin{itemize}
 \item \antigone, \baron, \couenne, \lindo, and \scip for \textit{QGQ};
 %
 \item \cplex for \textit{QGL} and \textit{CGC};
%
 \item \textcolor{red}{\gurobi and \xpress for \textit{QBC};}
%
 \item \bonmin, \gurobi, \knitro, \mosek, \sbb, and \xpress for \textit{CGC}.
\end{itemize}
%
We remark that \textcolor{red}{the solvers \bonmin, \knitro, and \sbb from} the latter category can be used as incomplete solvers for \textit{QGQ}. We also note that \lgo implements an incomplete BB algorithm for \textit{QCQ} by using bounds obtained from sampling.
